The hidden manifold distance for functional data

### 2019-07-30 index.Rmd

---
title: "The hidden manifold distance for functional data"
output:
  pdf_document:
    keep_tex: yes
    number_sections: yes
  word_document: default
  html_document:
    df_print: paged
    number_sections: yes
bibliography: references.bib
---

>>>>

---
title: "The hidden manifold distance for functional data"
output:
  word_document: default
  pdf_document:
    keep_tex: yes
    number_sections: yes
  html_document:
    df_print: paged
    number_sections: yes
bibliography: references.bib
---
